Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-07 Multiresolution_framework/ltx/manuscript.tex
added Viktor to the author list
just highlighted a sentence to discuss

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[UE,CU]{M. Dewar}
\ead{mike.dewar@columbia.edu}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt}
\author[DEEE]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. This is important for constructing the wavelets. For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.

>>>>

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{mike.dewar@columbia.edu}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. \parham{This is important for constructing the wavelets.} For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.
